---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# manager

[![Build Status](https://travis-ci.org/jentjr/manager.svg?branch=master)](https://travis-ci.org/jentjr/manager)
[![Build status](https://ci.appveyor.com/api/projects/status/wmatiqqb5e8v01lp/branch/master?svg=true)](https://ci.appveyor.com/project/jentjr/manager/branch/master)


`manager` provides a set of tools for plotting and analyzing groundwater data as
well as reading data from external sources such as MANAGES and gINT.

## Example
```{r, eval = FALSE}
data <- read_manages3("C:/path/to/Site.mdb")
```

## Installation

To install the `manager` package you must first make sure you have a working 
development environment.  
* **Windows**: Install [Rtools](http://cran.r-project.org/bin/windows/Rtools/).  
* **Mac**: Install Xcode from the Mac App Store.  
* **Linux**: Install a compiler and various development libraries (details vary across differnet flavors of Linux).  

Then, install the `devtools` package from CRAN with 
```R
install.packages("devtools")
```
After you have `devtools` installed you can install `manager` using the command 
```R
devtools::install_github("jentjr/manager")
```
Eventually, the package might be submitted to CRAN, but until then you'll have
to install with `devtools`.

## License
MIT