---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
devtools::load_all("/usr/local/src/manager")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

[![Build Status](https://travis-ci.org/jentjr/manager.svg?branch=master)](https://travis-ci.org/jentjr/manager)
[![Build status](https://ci.appveyor.com/api/projects/status/wmatiqqb5e8v01lp/branch/master?svg=true)](https://ci.appveyor.com/project/jentjr/manager/branch/master)
[![Coverage Status](https://img.shields.io/codecov/c/github/jentjr/manager/master.svg)](https://codecov.io/github/jentjr/manager?branch=master)

## Overview
The goal of manager is to provide a set of tools to simplify plotting and
analyzing environmental data that is in a [tidy format](https://cran.r-project.org/web/packages/tidyr/vignettes/tidy-data.html). Manager also provides 
functions to read data from external sources such as MANAGES and gINT.

## Example
```{r, eval = FALSE}
library(manager)

# reading data from external sources
data <- read_manages3("C:/path/to/Site.mdb")
```

```{r, time-series, fig.height=6, fig.width=9, results='hide', warning=FALSE}
# load example data and plot time series of selected wells and constituents
data("gw_data")

wells <- c("MW-1", "MW-2")

params <- c("Magnesium, dissolved", 
            "Sodium, dissolved", 
            "Chloride, total", 
            "Sulfate, total", 
            "Potassium, dissolved")

gw_data %>%
  filter(location_id %in% wells, param_name %in% params) %>%
  ts_plot(., facet_var = "param_name", group_var = "location_id")
```

```{r boxplots, fig.height=6, fig.width=9, results='hide'}
# create boxplots filled by gradient
gw_data %>%
  filter(param_name == "Chloride, total", 
         location_id %in% c("MW-1", "MW-2", "MW-3", "MW-4", "MW-5", "MW-6", "MW-7", "MW-8")) %>%
  mutate(gradient = if_else(location_id %in% wells, "upgradient", "downgradient")) %>% 
  boxplot(., fill = "gradient")
```

Piper Diagrams and more...
```{r, piper-plot, fig.height=6, fig.width=9, results='hide', warning=FALSE}
gw_data %>%
  piper_plot()
```

## Installation

To install the `manager` package you must first make sure you have a working 
development environment.

* **Windows**: Install [Rtools](http://cran.r-project.org/bin/windows/Rtools/).  
* **Mac**: Install Xcode from the Mac App Store.  
* **Linux**: Install a compiler and various development libraries (details vary across differnet flavors of Linux).  

Then, install the `devtools` package from CRAN with 
```R
install.packages("devtools")
```
After you have `devtools` installed you can install `manager` using the command 
```R
devtools::install_github("jentjr/manager")
```
Eventually, the package might be submitted to CRAN, but until then you'll have
to install with `devtools`.

## Shiny App

A [shiny app](http://shiny.rstudio.com) is included with the package. It can 
be launched locally by running `manager::manager()`, or you can browse to the
[shinyapps.io](http://shinyapps.io) website for 
[manager](http://jentjr.shinyapps.io/manager). In order to read a MANAGES, or 
gINT database you must be running a local server with `RODBC` installed. 
`R` must either be in 32-bit, or 64-bit mode depending on which drivers are installed for microsoft access. MANAGER has only been tested in 32-bit mode.
