<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Using the Groundwater Library}
-->

Using the Groundwater Library
========================================================

This document will aide in using the groundwater library for creating plots and analysing groundwater monitoring network data. 

The first section deals with loading data into R as well as cleaning and rearranging data for analysis. 

```{r}
# library(groundwater)
# gw_data <- connect_manages("H:/INTERNAL/MANAGES_DATA/Tanners/Tanners/Site.mdb")
# 
# head(gw_data)


# # files can also be read in .csv format
# card_data <- read.csv("/Users/justinjent/Downloads/MANAGES_data_long.csv", header=TRUE)
# 
# # this is the typical data format for groundwater monitoring
# head(card_data)


# lets select a few constituents
# unique(card_data$param_name) # get a list of the names
# 
# const <- c("Magnesium, Mg (dissolved)", "Manganese, Mn (dissolved)",
#            "Iron, Fe (dissolved)")
# 
# card_data_sub <- subset(card_data, param_name %in% const)

# we can cast the data with the reshape2 library
# library(reshape2)
# card_cast <- dcast(card_data_sub, value.var = "analysis_result",location_id + sample_date ~ param_name)

```

One thing that we might like to see is a plot of the correlations of the constituents. The PerformanceAnalytics library has a nice correlation chart. Let's plot the correlation matrix.

```{r fig.width=17, fig.height=11}
# library(PerformanceAnalytics)
# chart.Correlation(card_cast[-c(1:2)], method = "spearman", pch=21)
```

```{r}
# data(gw_data)
# data$sample_date <- as.POSIXct(data$sample_date, format="%Y-%m-%d")
# 
# #check wich wells and parameters only have one data point and remove those
# (check_data <- names(which(dlply(data, .(location_id, param_name), nrow) == 1)))
# 
# # remove PZ-1, PZ-2, Uranium, etc.
# wells_remove <- c("PZ-1", "PZ-2", "PZ-3", "PZ-4")
# param_remove <- c("Uranium, U", "Nitrate, NO3 as N","Nitrite, NO2, as N",
#                   "Nitrate-Nitrite, NO3-NO2, as N", "Se, diss", "SO4, tot",
#                   "Sb, diss")

# remove wells and parameter using %nin% from Hmisc pacakge
# library(Hmisc)
# data_comp <- subset(data, location_id %nin% wells_remove & param_name %nin% param_remove)

# check data again
# names(which(dlply(data_comp, .(location_id, param_name), nrow) == 1))
#  
# back <- as.POSIXct(c("2010-01-01","2012-01-01"), format="%Y-%m-%d")
# comp <- as.POSIXct(c("2012-02-01","2012-03-01"), format="%Y-%m-%d")

# lets use combo plot on only MW-1 and MW-2 to save output
# include <- c("MW-1", "MW-2")

# this time we use %in%
# data_comp <- subset(data_comp, location_id %in% include)

# use d_ply to create the plots
```
```{r fig.width=17, fig.height=11}
# d_ply(data_comp, .(location_id), combo_plot, back_date=back, comp_date=comp, .print=TRUE)
```

Test for geomchemistry_plots.r

```{r fig.width=17, fig.height=11}
# read in test data 
# data(gw_data)

# grab the variables needed from the file for the geochemistry plots
# plot_data <- get_plot_data(data)

# transform the data for a Piper plot
# piper_data <- transform_piper_data(plot_data) 

# Piper plot
# plots all wells for all dates
# plot_piper(piper_data)

## run the following to plot all wells by date
# d_ply(piper_data[!(piper_data$name %in% c("PZ-1", "PZ-2", "PZ-3", "PZ-4")),], .(date), plot_piper, .print = TRUE)

# # animated time plot using animation library
# piper_time_plot(piper_data) 

# # animated time plot saved to html
# piper_time_html(piper_data)

# # try to create a animated time plot of piper diagram using googleVis
# piper_time <- gvisMotionChart(piper_data, idvar = "name", timevar = "date", 
#                               xvar = "cation_x", yvar = "cation_y", 
#                               colorvar = "TDS")
# 
# plot(piper_time)

# transform data for Stiff Diagram
# stiff_data <- transform_stiff_data(plot_data)

# Stiff Diagram
# stiff_plot(stiff_data)

# # animation of Stiff Diagram
# stiff_time_plot(stiff_data)
# 
# # animated Stiff diagram saved to html
# stiff_time_html(stiff_data)

## run the following to print Stiff diagrams individually by date
# d_ply(stiff_data, .(sample_date), stiff_plot, .print = TRUE)

```